---
title: "Landscape of drug response biomarkers"
output:html_document
editor_options: 
  chunk_output_type: console
---

```{r}
set.seed(100)
```

Download all biomarkers data
```{r}
setwd('C:/Users/patipark/Dropbox/CCA project/CCA RNA-seq/NewGeneSet_Module_InitialAnalysis/prediction_function')

My.biomarkers <- read.csv('PredictedGenes_20191016.csv', header = TRUE, stringsAsFactors = FALSE)

My.biomarkers$Drug <- trimws(My.biomarkers$Drug,which = 'both')
```

Run data using Module_1.Rmd
Save drug sensitivity classification data
```{r}
# setwd('C:/Users/patipark/Dropbox/CCA project/CCA RNA-seq/NewGeneSet_Module_InitialAnalysis/Data_Module_3_1')
# write.csv(test, file = 'DrugSR_table_18022019.csv', row.names = FALSE, quote = FALSE)
```

Download drug sensitivity table, hallmarks and gene expression data
```{r}
setwd('C:/Users/patipark/Dropbox/CCA project/CCA RNA-seq/NewGeneSet_Module_InitialAnalysis/Data_Module_3_alldrugs_biomarkers')
df.explevel <- read.csv('Expression_level_ALL_20191111.csv', header = TRUE, stringsAsFactors = FALSE)

df.hallmark <- read.csv('Hallmarks_Matrix_20191111.csv', header = TRUE, stringsAsFactors = FALSE)

drugSR <- read.csv('Table_DrugSensitivityClass_20191009.csv', header = TRUE, stringsAsFactors = FALSE)

hallmark.category <- read.csv('Hallmark_Categories.csv', header = TRUE, stringsAsFactors = FALSE)

nodeSize <- read.csv('NodeSize_11072019.csv', header = TRUE, stringsAsFactors = FALSE)
```

Modify Cell line names and generate gene expression data table
```{r}
# Change cell names
require(tidyverse)
from <- c('KKU.213','KKU.214','KKU.156','HuCCA.1','RBE','KKK.D138','TFK.1','YSCCC','SSP.25','KKU.100','HuCCT.1','KKK.D131','KKU.055','KKK.D068','HuH.28')

to <- c('KKU-213','KKU-214','KKU-156','HuCCA-1','RBE','KKK-D138','TFK-1','YSCCC','SSP-25','KKU-100','HuCCT-1','KKK-D131','KKU-055','KKK-D068','HuH-28')

map <- setNames(to,from)

# rename cell names in df.explevel
ln.col <- length(colnames(df.explevel))
b <- lapply(1:ln.col, function(n) {
  idx.name <- which(colnames(df.explevel) %in% names(map))
  if (n %in% idx.name){
    a <- as.data.frame(df.explevel[,c(n)])
    colnames(a)[1] <- map[which(names(map) == colnames(df.explevel)[n])]
  } else {
    a <- as.data.frame(df.explevel[,c(n)])
    colnames(a)[1] <- colnames(df.explevel)[n]
  }
  return(a)
})
# mRNA expression levels as in fold-change
b.out <- do.call(cbind,b) %>% reshape2::melt(., id.vars = 'Gene', 
                                             variable.name = 'Cell', 
                                             value.name = 'exp.fc')
# prepare drug response table
my.drugSR <- drugSR %>% subset(Cell %in% to)
```

Add category to hallmarks
```{r}
hallmark.category <- hallmark.category %>% distinct(.,ID,Hallmark.Category,.keep_all = TRUE)
# create a vector by matching ID names
Hallmark.cat <- hallmark.category$Hallmark.Category[match(df.hallmark$ID,hallmark.category$ID)]
# add to df.input data table
df.hallmark<- tibble::add_column(df.hallmark, Hallmark.cat, .before = 0)
df.hallmark$Cell <- gsub('_S.R','',df.hallmark$Cell) %>% trimws(., which = c('both'))
```

Save data as Hallmarks_Matrix_07042019.csv
```{r}
setwd('C:/Users/patipark/Dropbox/CCA project/CCA RNA-seq/NewGeneSet_Module_InitialAnalysis/Data_Module_3_alldrugs_biomarkers')
# write.csv(df.input,'Hallmarks_Matrix_07042019.csv', row.names = FALSE, quote = FALSE )
```

Extract candidate gene list for first drug
```{r}
# All drugs are ranked by their node size.
all.drug <- nodeSize$agent
# but not all drugs are used in biomarker analysis
drugBio <- unique(My.biomarkers$Drug)

int.drug <- intersect(all.drug,drugBio)

newDrug <- c('Subtype_1.2','OrgSubtype_1.2', int.drug)
```

PAM50 and CCA45
```{r}
PAM50 <- c('SLC39A6','MDM2','MYC','MLPH','CXXC5','BAG1','FOXA1','CENPF','MMP11','BLVRA',
'ERBB2','PHGDH','RRM2','ESR1','KRT17','BIRC5','FOXC1','CCNB1','PTTG1','GPR160',
'KRT5','UBE2C','SFRP1','ACTR3B','MKI67','TYMS','CDH3','MAPT','PGR','CEP55',
'ANLN','BCL2','MELK','CDC6','MYBL2','KRT14','EGFR','FGFR4','NAT1','EXO1',
'GRB7','CDC20','TMEM45B','ORC6L','MIA','UBE2T','CCNE1','CDCA1','KNTC2','KIF2C')

CCA45 <- c('PHLDA3','NOTCH1','PUS1','VEGFC','FDXR','RRAD','ITGB4','NADSYN1','NCBP1','PHLDA2','TUFM','ELF3','COX6C','DCTPP1','KLF4','SATB1','KRT15','ATF3','CD9','DUSP5','IER2','MYC','TNFAIP2','FBLN1','ISCU','JAG2','RAD23B','TP53','TSPAN1','BTG2','FGFR3','CAV1','COL12A1','FOS','PTGER4','RALGDS','RHOD','UPP1','IL4R','ITGB2','LSM7','TCOF1','AREG','TP63','HR')

intersect(PAM50,CCA45)

```

Create S3 data that contain the followings:
1. Gene candidates and their hallmark annotation of individual drug treatment
2. Gene expression levels of individual drug treatment
3. Drug sensitivity and GR50 values of individual drug treatment
```{r}
# extract gene expression using genes from the list
SS.df <- lapply(1:length(newDrug), function(x) {
  sel.drug <- newDrug[x]
  # sel.drug <- 'Subtype_1.2'
  # if(sel.drug != 'Subtype_1.2'){
  #   sel.drug <- 'CCA Subgroup' #paste0(sel.drug,'_S.R')
  # }
  genelist <- My.biomarkers %>% subset(Drug %in% sel.drug) %>% dplyr::select('Gene')

  # Plot a heatmap of selected genes
  predgenes <- genelist$Gene
  # require gene expression table (b.out)
  dtexp.m <- b.out %>% subset(Cell %in% to)
  # prepare data for pheatmap
  # to is a list of CCA cell lines with official names
  temp <- dtexp.m %>% subset(Gene %in% predgenes) %>% as.data.frame()
  
  # rearrange cell lines in the order of Subtype 1 and 2
  # define order of cell lines in subgroup 1
  # from drugSR table
  if(sel.drug == 'Subtype_1.2') {
    # S1 = CCA1
    S1 <- c('KKU-213','KKU-214','KKU-156','HuCCA-1','RBE','KKK-D138')
    # S2 = CCA2
    S2 <- c('TFK-1','YSCCC','SSP-25','KKU-100','HuCCT-1','KKK-D131','KKU-055','KKK-D068','HuH-28')
    listSR <- 'Subtype_1.2'
  } else if (sel.drug == 'OrgSubtype_1.2') {
    # S1 = Pancreas-like
    S1 <- c('KKU-213','KKU-214','KKU-156','HuCCA-1','TFK-1','YSCCC','HuCCT-1','KKK-D131')
    # S2 = Liver-like
    S2 <- c('RBE','KKK-D138','SSP-25','KKU-100','KKU-055','KKK-D068','HuH-28')
    listSR <- 'OrgSubtype_1.2'
  } else {
    drug1 <- gsub('_S.R','',sel.drug)
    drug.name <- gsub(pattern = '\\.',replacement = '-',drug1)
    listSR <- my.drugSR %>% subset(Drug %in% drug.name)
    # log 10 transform GR50 for normal distribution
    listSR$log10GR50 <- log10(listSR$GR50 + 4)
    my.S1 <- listSR %>% subset(CCA.Subgroup == 'Subgroup 1') %>% arrange(-(log10GR50))
    my.S2 <- listSR %>% subset(CCA.Subgroup == 'Subgroup 2') %>% arrange(-(log10GR50)) 
    # extract cell line names arranged in order of ascending GR50 
    S1 <- my.S1$Cell
    S2 <- my.S2$Cell
  }
  
  # arrange columns using indices
  # require(reshape2)
  sel.h2 <- temp %>% subset(Cell %in% c('Gene',S1,S2)) %>% reshape2::dcast(., Gene ~ Cell, var = 'exp.fc')
  sel.h2 <- sel.h2[,c('Gene',S1,S2)] %>% tibble::column_to_rownames(., var = 'Gene')
  
  ### annotate candidate genes with hallmark name and category
  # call genes from core_enrichment
  sel.h <- tibble::rownames_to_column(sel.h2, var = 'Gene')
  # add drug annotation
  Drug <- rep(sel.drug,nrow(sel.h))
  sel.h <- tibble::add_column(sel.h, Drug, .before = 0)
  # subset df.hallmark to limit only drug of interest
  if(sel.drug == 'Subtype_1.2'){
    df.hm <- df.hallmark %>% subset(Cell == 'Subtype_1.2')
  } else if (sel.drug == 'OrgSubtype_1.2'){
    df.hm <- df.hallmark %>% subset(Cell == 'OrgSubtype_1.2')
  } else {
    df.hm <- df.hallmark %>% subset(Cell == sel.drug)
  }
  S <- lapply(1:length(sel.h$Gene), function(j) {
    A <- lapply(1:nrow(df.hm), function(i) {
      ss <- df.hm$core_enrichment[i]
      # split string list
      ss2 <- strsplit(ss,split = '/')
      ss.df <- data.frame('Gene' = do.call(cbind,ss2))
      # find whether the gene from selected gene list is in the core_enrichment
      if (sel.h$Gene[j] %in% ss.df$Gene) {
        data.frame('Gene' = sel.h$Gene[j],
                   # 'Hallmark.Category' = df.hm$Hallmark.cat[i],
                   'Hallmark.ID' = df.hm$ID[i],
                   'Cell' = df.hm$Cell[i],
                   'pvalue' = df.hm$pvalue[i],
                   'p.adjust' = df.hm$p.adjust[i],
                   'qvalues' = df.hm$qvalues[i]
        )
      } else {
        data.frame('Gene' = sel.h$Gene[j],
                   # 'Hallmark.Category' = NA,
                   'Hallmark.ID' = NA,
                   'Cell' = NA,
                   'pvalue' = NA,
                   'p.adjust' = NA,
                   'qvalues' = NA
        )
      }
    })
    # build dataframe
    AA <- do.call(rbind,A)
    # get unique genes
    uAA <- unique(AA)
    # remove NA rows
    H <- uAA[!is.na(uAA$Hallmark.ID),]
  })
  GeneHallmark <- do.call(rbind,S)
  # screeen hallmark that has pvalue < 0.01 or p.adjust < 0.05 and qvalues < 0.25
  GeneHallmark.filtered <- GeneHallmark %>% subset(p.adjust < 0.05)
  if (nrow(GeneHallmark.filtered) == 0){
    GeneHallmark.filtered <- GeneHallmark.filtered %>% subset(pvalue < 0.1)
  }
  # add MeanDecreaseAccuracy and MeanDecreaseGini
  # S.df$MeanDecreaseGini <- genelist$MeanDecreaseGini[match(S.df$Gene,genelist$Gene)]
  colnames(GeneHallmark.filtered)[which(colnames(GeneHallmark.filtered) == 'Cell')] <- 'Drug'
  # drug sensitivity from listSR
  DrugSensitivity <- listSR
  
  outputs <- list('Hallmarks' = GeneHallmark.filtered,
                  'GeneExpression' = sel.h,
                  'DrugSensitivity' = listSR)
  return(outputs)
})
```

Coerce into data tables of gene/hallmark, gene expression, drug sensitivity
```{r}
allHallmarks<- do.call(rbind,lapply(1:length(SS.df), function(x) SS.df[[x]]$Hallmarks))
allGeneExpression <- do.call(rbind,lapply(1:length(SS.df), function(x) SS.df[[x]]$GeneExpression))

allDrugSensitivity <- do.call(rbind,lapply(1:length(SS.df), function(x) SS.df[[x]]$DrugSensitivity))

# # mean gene expr values
# allGeneExpression <- reshape2::melt(allGeneExpression, id.vars = c('Gene','Drug'), variable.name = c('Cell'), value.name = c('expr'))
# # calculate mean expression level of gene in a cell if
# allGeneExpression <- allGeneExpression %>% group_by(Gene,Cell) %>% summarise(expr = mean(expr))
# allGeneExpression <- reshape2::dcast(allGeneExpression, Gene ~ Cell, value.var = 'expr')
# # now, we have a table of expression level of gene per cell line
```

Use ComplexHeatmap to plot figure 4B and S5A.
```{r}
# draw.hm <- function(x) {
ClassifierGenes <- lapply(1:length(newDrug), function(x) {
  # for(x in 1:length(DrugInit)) {
  # select tested drug x
  my.drug <- newDrug[x]
  if(my.drug == 'Subtype_1.2') {
    S1 <- c('KKU-213','KKU-214','KKU-156','HuCCA-1','RBE','KKK-D138')
    S2 <- c('TFK-1','YSCCC','SSP-25','KKU-100','HuCCT-1','KKK-D131','KKU-055','KKK-D068','HuH-28')
    Sall <- c(S1,S2)
    my.drug.biom <- my.drug
    coldat <- data.frame('Cell' = Sall,
                         'CCA.Subgroup' = ifelse(Sall %in% S1,'Subgroup 1','Subgroup 2'))
  } else if (my.drug == 'OrgSubtype_1.2') {
    S1 <- c('KKU-213','KKU-214','KKU-156','HuCCA-1','TFK-1','YSCCC','HuCCT-1','KKK-D131')
    S2 <- c('RBE','KKK-D138','SSP-25','KKU-100','KKU-055','KKK-D068','HuH-28')
    Sall <- c(S1,S2)
    my.drug.biom <- my.drug
    coldat <- data.frame('Cell' = Sall,
                         'CCA.Subgroup' = ifelse(Sall %in% S1,'Subgroup 1','Subgroup 2'))
  } else {
    # define S1 and S2 using data from allDrugSensitivity
    S1.df <- allDrugSensitivity %>% subset(Drug %in% my.drug & DrugSensitivity.kde %in% c('Sensitive')) %>% group_by(GR50) %>% arrange(.,-desc(GR50))
    S2.df <- allDrugSensitivity %>% subset(Drug %in% my.drug & DrugSensitivity.kde %in% c('Resistant')) %>% group_by(GR50) %>% arrange(.,-desc(GR50))
    S1 <- S1.df$Cell
    S2 <- S2.df$Cell
    # collect cell lines from Subgroup 1 (drug sensitive) and Subgroup 2 (drug resistant)
    Sall <- c(S1,S2)
    my.drug.biom <- paste0(my.drug,'_S.R')
    # GR50 data table
    coldat <- rbind(S1.df,S2.df)
  }
  # subset gene expression data
  my.dt <- allGeneExpression %>% subset(Drug == my.drug) %>% dplyr::select(-Drug) %>% `rownames<-`(.,NULL) %>% tibble::column_to_rownames(., var = 'Gene')
  
  # rearrange columns by order of cells from tested drug
  my.dt <- my.dt[,Sall]
  # subset genes specific to a particular drug
  my.genelist <- My.biomarkers %>% subset(Drug == my.drug) %>% arrange(desc(test.ROC.AUC),desc(Varimp.Score)) #subset(Drug %in% my.drug.biom)
  # arrange rownames according to my.genelist$Gene
  my.dt <- my.dt[match(my.genelist$Gene,rownames(my.dt)),]
  # remove NA rows
  my.dt <- my.dt[complete.cases(my.dt), ]
  
  # rank gene expression level in each cell line by important score of the genes
  my.dt.sorted <- my.dt
  # color scale
  my.colorgradient3 <- rev(c('#67001f','#b2182b','#d6604d','#f4a582','#ffffff','#92c5de','#4393c3','#2166ac','#053061'))
  
  # filter out non-significant genes using wilcox.test (Mann-Whitney)
  # keep both significant and non-significant genes
  # rearrange rownames to column 'Gene'
  dt.temp <- tibble::rownames_to_column(my.dt.sorted, var = 'Gene')
  # reshape data frame
  sig.test <- reshape2::melt(dt.temp,id.vars = c('Gene'), variable.name = c('Cell'), value.name = c('expr'))
  # assign CCA.subgroup to cell
  sig.test$Subgroup <- ifelse(sig.test$Cell %in% S1,'Sensitive','Resistant')
  # caluculate Mann-Whitney p-value (unpaired) of expression by group per gene
  set.seed(100)
  sum.sig.test <- sig.test %>% group_by(Gene) %>% 
    summarise(wilcox.pvalue = wilcox.test(expr ~ Subgroup,
                                          exact = FALSE, 
                                          correct = TRUE,
                                          paired = FALSE)$p.value
    )
  
  # calculate avaraged expression level
  sum.genes <- sig.test %>% group_by(Gene) %>% 
    summarise(mean.CCA1 = mean(expr[Subgroup == 'Sensitive']),
              mean.CCA2 = mean(expr[Subgroup == 'Resistant'])) %>%
    mutate(ratio = mean.CCA1 / mean.CCA2)
  
  # add p-value to the table
  sum.genes$wilcox.pvalue <- sum.sig.test$wilcox.pvalue[match(sum.genes$Gene,sum.sig.test$Gene)]
  
  # identify genes with p-value < 0.05 when compared between Sensitive and Resistant groups
  ha.row.df <- sum.genes %>% subset(wilcox.pvalue < 0.05) %>% arrange(desc(-wilcox.pvalue))
  # if p > 0.05
  if (nrow(ha.row.df) == 0) {
    ha.row.df <- sum.genes %>% subset(wilcox.pvalue < 0.1) %>% arrange(desc(-wilcox.pvalue))
  } 
  if (nrow(ha.row.df) == 0) {
    ha.row.df <- sum.genes %>% subset(wilcox.pvalue < 0.15) %>% arrange(desc(-wilcox.pvalue))
  } 
  if (nrow(ha.row.df) == 0) {
    ha.row.df <- sum.genes %>% subset(wilcox.pvalue < 0.2) %>% arrange(desc(-wilcox.pvalue))
  }
  
  # subset significantly expressed genes from expression data table
  sig.test <- sig.test %>% subset(Gene %in% ha.row.df$Gene)
  
  # add VIP score from random forest model
  sig.VIP <- extractVIP(sig.test)
  
  # add VIP score from random forest model
  ha.row.df$VIP.rf <- sig.VIP$VIP.rf[match(ha.row.df$Gene,sig.VIP$Gene)]
  
  # add prediction accuracy from random forest model
  ha.row.df$Accuracy.rf <- sig.VIP$Accuracy.rf[match(ha.row.df$Gene,sig.VIP$Gene)]
  
  # add VIP score from PLSDA
  ha.row.df$VIP.plsda <- sig.VIP$VIP.plsda[match(ha.row.df$Gene,sig.VIP$Gene)]
  
  # add prediction accuracy from PLSDA
  ha.row.df$Accuracy.plsda <- sig.VIP$Accuracy.plsda[match(ha.row.df$Gene,sig.VIP$Gene)]
  
  # add drug label
  ha.row.df$Drug <- my.drug
  
  my.dt2 <- my.dt.sorted[c(ha.row.df$Gene),]
  
  my.dt2$Drug <- my.drug
  
  output <- list('Gene.summary' = ha.row.df,
                 'Gene.expr' = my.dt2)
  
  return(output)
  
})

# create table
Classifier.genes <- do.call(rbind,lapply(1:length(ClassifierGenes), function(x) ClassifierGenes[[x]]$Gene.summary))

Expression.genes <- do.call(rbind,lapply(1:length(ClassifierGenes), function(x) ClassifierGenes[[x]]$Gene.expr))

```  

Save the two tables
```{r}
setwd('C:/Users/patipark/Dropbox/CCA project/CCA RNA-seq/NewGeneSet_Module_InitialAnalysis/Figure_4A_files')

# write.csv(Classifier.genes, file = 'ListOfClassifierGenes.csv', row.names = FALSE)

# write.csv(Expression.genes, file = 'ExpressionOfClassifierGenes.csv', row.names = FALSE)
```

Find VIP score using caret's random forest model
X = gene expression of drug sensitive and resistant groups of cell lines
Y = sensitive or resistant
```{r}
# function for getting VIP score and accuracy 
extractVIP <- function(sig.test){
  # 1.
  # create X input table
  dat.X <- reshape2::dcast(sig.test, Cell+Subgroup ~ Gene, value.var = 'expr',fun.aggregate = mean) %>% 
    tibble::column_to_rownames(., var = 'Cell')
  
  # create Y input table
  dat.Y <- reshape2::dcast(sig.test, Cell ~ Subgroup, value.var = 'Subgroup')
  dat.Y$Subgroup <- ifelse(dat.Y$Sensitive != 0, 'Sensitive','Resistant')
  dat.Y <- dat.Y %>% dplyr::select(Cell,Subgroup)
  
  # add factor level
  dat.Y$Subgroup <- factor(dat.Y$Subgroup, levels = c('Sensitive','Resistant'))
  dat.X$Subgroup <- factor(dat.X$Subgroup, levels = c('Sensitive','Resistant'))
  
  # get number of cell lines in each group
  # drug sensitive group
  Sen.group <- dat.Y %>% subset(Subgroup == 'Sensitive')
  
  Sen.number <- ceiling(nrow(Sen.group)*0.7)
  # drug resistant group
  Res.group <- dat.Y %>% subset(Subgroup == 'Resistant')
  
  Res.number <- ceiling(nrow(Res.group)*0.7)
  
  # set the minimum number of each group to 3
  if(Sen.number < 3 | Res.number < 3) {
    n.Sampling <- 3
  } else {
    n.Sampling <- min(Sen.number,Res.number)
  }
  
  # random sample sensitive group
  if(nrow(Sen.group) < 3) {
    
    S.set <- dat.X %>% subset(rownames(.) %in% Sen.group$Cell)
    S.set <- S.set[rep(row.names(S.set), 2),]
    
  } else {
    set.seed(100)
    S.set <- dat.X %>% tibble::rownames_to_column(., var = 'Cell') %>% 
      subset(Cell %in% Sen.group$Cell) %>% 
      sample_n(., size = n.Sampling) %>%
      `rownames<-`(.,NULL) %>%
      tibble::column_to_rownames(., var = 'Cell')
    
  } 
  # random sample resistant group
  if(nrow(Res.group) < 3) {
    
    R.set <- dat.X %>% subset(rownames(.) %in% Res.group$Cell)
    R.set <- R.set[rep(row.names(R.set), 2),]
    
  } else {
    set.seed(100)
    R.set <- dat.X %>% tibble::rownames_to_column(., var = 'Cell') %>% 
      subset(Cell %in% Res.group$Cell) %>% 
      sample_n(., size = n.Sampling) %>%
      `rownames<-`(.,NULL) %>%
      tibble::column_to_rownames(., var = 'Cell')
    
  } 
  
  # combine sensitive and resistant cells to a training dataset
  trainingX <- rbind(S.set,R.set)
  
  # 2. build training model for random forest model
  require(caret)
  set.seed(100)
  control <- caret::trainControl(method = 'LOOCV', # limit to 50-100 repeats
                                 # number = 10,
                                 # repeats = 10,
                                 savePredictions = 'all',
                                 classProbs = TRUE,
                                 summaryFunction = twoClassSummary
  )

  #Number randomely variable selected is mtry
  mtry <- floor(sqrt(ncol(trainingX)))
  
  tunegrid <- expand.grid(.mtry = mtry)
  
  rf_default <- caret::train(Subgroup ~ ., 
                             data = trainingX, 
                             method  ='rf', 
                             metric = 'ROC',
                             tuneGrid = tunegrid, 
                             trControl = control)
  
  # 3.test the prediction model using testing data set
  # remove Subgroup column
  testingX <- dat.X %>% tibble::rownames_to_column(., var = 'Cell') %>% 
    subset(!Cell %in% rownames(trainingX)) %>% 
    `rownames<-`(., NULL) %>%
    tibble::column_to_rownames(., var = 'Cell') %>%
    dplyr::select(-one_of('Subgroup'))
  
  # predict subclasses from expr using rf model
  testResult <- predict(rf_default, 
                        testingX, 
                        type = 'prob') %>% as.data.frame()
  # based on probability
  testResult$pred <- ifelse(testResult$Sensitive > testResult$Resistant, 'Sensitive','Resistant')
  
  # add actual response
  actual.resp <- dat.X %>% tibble::rownames_to_column(., var = 'Cell') %>% 
    subset(!Cell %in% rownames(trainingX)) %>% 
    dplyr::select(Cell,Subgroup)
  
  # add to testResult
  testResult$resp <- actual.resp$Subgroup[match(rownames(testResult), actual.resp$Cell)]
  
  # change to numeric
  testResult$pred <- ifelse(testResult$pred == 'Sensitive', 1, 2)
  testResult$resp <- ifelse(testResult$resp == 'Sensitive', 1, 2)
  
  # add factor levels
  testResult$pred <- factor(testResult$pred, levels = c(1,2))
  testResult$resp <- factor(testResult$resp, levels = c(1,2))
  
  # 4. calculate prediction accuracy
  accuracy <- caret::confusionMatrix(data = testResult$pred,
                         reference = testResult$resp)$overall[1]
  
  # extract VIP score from random forest model
  drug.VIP <- caret::varImp(rf_default, scale = TRUE)$importance
  drug.VIP <- tibble::rownames_to_column(drug.VIP, var = 'Gene')
  
  # change column names
  colnames(drug.VIP) <- c('Gene','VIP.rf')
  
  # add accuracy values
  drug.VIP$Accuracy.rf <- as.numeric(accuracy)
  
  # 5. calculate VIP score using PLSR
  set.seed(100)
  pls.model <- caret::plsda(x = trainingX[,-c(1)], 
                            y = as.factor(trainingX[,c(1)]),
                            # ncomp = 5,
                            probMethod = 'softmax')

  # test accuracy
  pls.result <- predict(pls.model, testingX, type = 'prob') %>% as.data.frame()
  
  # change column names
  colnames(pls.result) <- c('Sensitive','Resistant')
  
  # predicted response
  pls.result$pred <- ifelse(pls.result$Sensitive > pls.result$Resistant, 'Sensitive','Resistant')
  
  # actual response 
  real.resp <- dat.X %>% tibble::rownames_to_column(., var = 'Cell') %>% 
    subset(Cell %in% rownames(testingX)) %>% 
    dplyr::select(Cell,Subgroup)
  
  # real response
  pls.result$resp <- real.resp$Subgroup[match(rownames(pls.result),real.resp$Cell)]
  
  # add factor levels
  pls.result$pred <- factor(pls.result$pred, levels = c('Sensitive','Resistant'))
  pls.result$resp <- factor(pls.result$resp, levels = c('Sensitive','Resistant'))
  
  # calculate prediction accuracy
  pls.accuracy <- caret::confusionMatrix(data = pls.result$pred,
                         reference = pls.result$resp)$overall[1]
  
  # extract VIP score from PLSDA model
  VIP.pls <- caret::varImp(pls.model)
  
  # scale VIP score to 0-100
  VIP.pls2 <- VIP.pls %>% mutate(Gene = rownames(.),
                                 VIP.plsda = ((Overall - min(Overall)) / (max(Overall) - min(Overall)))*100) %>%
    dplyr::select(Gene,VIP.plsda)
  
  # add VIP to drug.VIP
  drug.VIP$VIP.plsda <- VIP.pls2$VIP.plsda[match(drug.VIP$Gene,VIP.pls2$Gene)]
  drug.VIP$Accuracy.plsda <- pls.accuracy
  
  return(drug.VIP)

  }

```

Draw Figure 4A 
```{r}
# make table for ComplexHeatmap annotation
ColDat <- lapply(1:length(newDrug), function(x) {
  my.drug <- newDrug[x]
  if(my.drug == 'Subtype_1.2') {
    S1 <- c('KKU-213','KKU-214','KKU-156','HuCCA-1','RBE','KKK-D138')
    S2 <- c('TFK-1','YSCCC','SSP-25','KKU-100','HuCCT-1','KKK-D131','KKU-055','KKK-D068','HuH-28')
    Sall <- c(S1,S2)
    my.drug.biom <- my.drug
    coldat <- data.frame('Cell' = Sall,
                         'GR50' = NA,
                         'Class.mc' = NA,
                         'Class.kde' = NA,
                         'DrugSensitivity.mc' = NA,
                         'DrugSensitivity.kde' = NA,
                         'CCA.Subgroup' = ifelse(Sall %in% S1,'Subgroup 1','Subgroup 2'),
                         'Drug' = 'Subtype_1.2',
                         'log10GR50' = NA
                         )
  } else if (my.drug == 'OrgSubtype_1.2') {
    S1 <- c('KKU-213','KKU-214','KKU-156','HuCCA-1','TFK-1','YSCCC','HuCCT-1','KKK-D131')
    S2 <- c('RBE','KKK-D138','SSP-25','KKU-100','KKU-055','KKK-D068','HuH-28')
    Sall <- c(S1,S2)
    my.drug.biom <- my.drug
    coldat <- data.frame('Cell' = Sall,
                         'GR50' = NA,
                         'Class.mc' = NA,
                         'Class.kde' = NA,
                         'DrugSensitivity.mc' = NA,
                         'DrugSensitivity.kde' = NA,
                         'CCA.Subgroup' = ifelse(Sall %in% S1,'Subgroup 1','Subgroup 2'),
                         'Drug' = 'OrgSubtype_1.2',
                         'log10GR50' = NA
                         )
  } else {
    # define S1 and S2 using data from allDrugSensitivity
    S1.df <- allDrugSensitivity %>% subset(Drug %in% my.drug & DrugSensitivity.kde %in% c('Sensitive')) %>% group_by(GR50) %>% arrange(.,-desc(GR50))
    S2.df <- allDrugSensitivity %>% subset(Drug %in% my.drug & DrugSensitivity.kde %in% c('Resistant')) %>% group_by(GR50) %>% arrange(.,-desc(GR50))
    S1 <- S1.df$Cell
    S2 <- S2.df$Cell
    # collect cell lines from Subgroup 1 (drug sensitive) and Subgroup 2 (drug resistant)
    Sall <- c(S1,S2)
    my.drug.biom <- paste0(my.drug,'_S.R')
    # GR50 data table
    coldat <- as.data.frame(rbind(S1.df,S2.df))
  }
})

ColDat <- do.call(rbind, ColDat)

```

Save table DrugSenstivity by KDE
```{r}
# setwd('C:/Users/patipark/Dropbox/CCA project/CCA RNA-seq/NewGeneSet_Module_InitialAnalysis/Figure_4A_files')
# 
# write.csv(ColDat, file = 'DrugSensitivityByKDE.csv', row.names = FALSE)
```


```{r}
require(ComplexHeatmap)
# Modify Column annotations
coldat <- ColDat %>% subset(Drug %in% my.drug) %>% as.data.frame()

if (my.drug == 'Subtype_1.2'){
  df <- coldat %>% dplyr::select(Cell,CCA.Subgroup) %>% 
    `rownames<-`(.,NULL) %>% 
    tibble::column_to_rownames(., var = 'Cell')
  ha <- ComplexHeatmap::HeatmapAnnotation(df = df,
                          col = list(CCA.Subgroup = c('Subgroup 1' = 'cyan','Subgroup 2' = 'orange')),
                          gap = unit(c(2),'mm'),
                          show_annotation_name = TRUE,
                          # annotation_name_gp = gpar(fontsize = 7, family = 'Arial'),
                          annotation_name_side = 'left',
                          annotation_legend_param = list(
                            direction = 'horizontal')
  )
} else if (my.drug == 'OrgSubtype_1.2') {
  df <- coldat %>% dplyr::select(Cell,CCA.Subgroup) %>% 
    `rownames<-`(.,NULL) %>% 
    tibble::column_to_rownames(., var = 'Cell')
  ha <- ComplexHeatmap::HeatmapAnnotation(df = df,
                          col = list(CCA.Subgroup = c('Subgroup 1' = 'darkolivegreen','Subgroup 2' = 'firebrick4')),
                          gap = unit(c(2),'mm'),
                          show_annotation_name = TRUE,
                          # annotation_name_gp = gpar(fontsize = 7, family = 'Arial'),
                          annotation_name_side = 'left',
                          annotation_legend_param = list(
                            direction = 'horizontal')
  )
  
} else {
  # data frame to plot log10GR50 bars
  df <- coldat %>% `rownames<-`(., NULL) %>% 
    tibble::column_to_rownames(., var = 'Cell') %>% 
    dplyr::select(DrugSensitivity.kde)
  colnames(df) <- c('Drug.Sensitivity')
  ha <- ComplexHeatmap::HeatmapAnnotation(df = df,
                          col = list(Drug.Sensitivity = c('Sensitive' = 'darkolivegreen', 'Resistant' = 'firebrick4')
                                     # CCA.Subgroup = c('Subgroup 1' = 'cyan','Subgroup 2' = 'orange')
                          ),
                          gap = unit(c(2), 'mm'),
                          annotation_legend_param = list(direction = 'horizontal',
                                                         nrow = 1),
                          # gp = gpar(fill = ifelse(coldat$Cell %in% CCA.S1,'cyan','orange'))),
                          # annotation_height = unit.c(unit(2, 'cm'), unit(2, 'cm'), unit(2, 'cm')),
                          show_annotation_name = TRUE,
                          # annotation_name_gp = gpar(fontsize = 7, family = 'Arial'),
                          annotation_name_side = 'left'
                          # annotation_name_rot = c(0)
  )
}

# expression data tabke
dset.cca <- Expression.genes %>% subset(Drug %in% my.drug)

# create clinical data
clinical.data.cca <- data.frame('ID' = to)

# non-OV cell lines
nonfluke <- c('RBE','SSP-25','YSCCC','HuH-28','TFK-1','HuCCT-1')

# liver-like cell lines
liver <- c('RBE','HuH-28','KKU-100','KKK-D138','KKK-D068','KKU-055','SSP-25')

# compose clinical data
clinical.data.cca <- clinical.data.cca %>% 
  mutate(OrganSubtype = case_when(ID %in% liver ~ 'Liver-like',
                                  TRUE ~ 'Pancrease-like'),
         Fluke.Infection = case_when(ID %in% nonfluke ~ 'Fluke-neg',
                                     TRUE ~ 'Fluke-pos'),
         DrugSubtype = case_when(ID %in% to[1:6] ~ 'CCA1',
                                 TRUE ~ 'CCA2'),
         Country = case_when(ID %in% nonfluke ~ 'Japan',
                             TRUE ~ 'Thailand'))

# add factor levels to clinical.data.cca
clinical.data.cca$Fluke.Infection <- factor(clinical.data.cca$Fluke.Infection,
                                            levels = c('Fluke-pos','Fluke-neg'))

clinical.data.cca$Country <- factor(clinical.data.cca$Country,
                                    levels = c('Thailand','Japan'))

clinical.data.cca$DrugSubtype <- factor(clinical.data.cca$DrugSubtype,
                                        levels = c('CCA1','CCA2'))

clinical.data.cca$OrganSubtype <- factor(clinical.data.cca$OrganSubtype,
                                         levels = c('Liver-like','Pancrease-like'))

clinical.data.cca <- tibble::column_to_rownames(clinical.data.cca, var = 'ID')

## Create row annotation
rowdat <- Classifier.genes %>% subset(Drug %in% my.drug)

# For CCA subgroups, we group genes COL12A1,VEGFC,FBLN1 as 'Neg'
rowdat$Group <- ifelse(rowdat$Gene %in% c('COL12A1','VEGFC','FBLN1'),'Neg','Pos')
rowdat$Group <- factor(rowdat$Group, levels = c('Pos','Neg'))

```

```{r}
# # rearrange genes by group and dimeCor
# rowdat.Pos <- rowdat %>% subset(Group == 'Pos') %>% arrange(-ratio)
# rowdat.Neg <- rowdat %>% subset(Group == 'Neg') %>% arrange(-ratio)
# rowdat <- rbind(rowdat.Pos, rowdat.Neg)

# rearrange genes by p-value and dimeCor
rowdat.Pos <- rowdat %>% subset(Group == 'Pos') %>% arrange(wilcox.pvalue)
rowdat.Neg <- rowdat %>% subset(Group == 'Neg') %>% arrange(-wilcox.pvalue)
rowdat <- rbind(rowdat.Pos, rowdat.Neg)

# make sure that genes in rows were arranged by Gini score from high to low
ha.row.VIPrf <- ComplexHeatmap::rowAnnotation(VIP.rf = anno_barplot(rowdat$VIP.rf, which = 'row',
                                                 gp = gpar(fill = 'black'),
                                                 # ylim = c(0,0.05),
                                                 axis_param = list(gp = gpar(fontsize = 5,
                                                                             family = 'Arial'),
                                                                   side = 'bottom'),
                                                 # axis_direction = 'normal', # 'reverse'
                                                 axis = TRUE),
                              width = unit(1.5, 'cm'),
                              show_annotation_name = TRUE,
                              annotation_legend_param = list(direction = 'horizontal', nrow = 1),
                              annotation_name_gp = gpar(fontsize = 10),
                              annotation_name_offset = unit(c(6), 'mm'),
                              annotation_name_rot = c(0)
)

ha.row.VIPplsda <- ComplexHeatmap::rowAnnotation(VIP.pls = anno_barplot(rowdat$VIP.plsda, which = 'row',
                                                       gp = gpar(fill = 'black'),
                                                       # ylim = c(0,0.05),
                                                       axis_param = list(gp = gpar(fontsize = 5,
                                                                                   family = 'Arial'),
                                                                         side = 'bottom'),
                                                       # axis_direction = 'normal', # 'reverse'
                                                       axis = TRUE),
                                 width = unit(1.5, 'cm'),
                                 show_annotation_name = TRUE,
                                 annotation_legend_param = list(direction = 'horizontal', nrow = 1),
                                 annotation_name_gp = gpar(fontsize = 10),
                                 annotation_name_offset = unit(c(6), 'mm'),
                                 annotation_name_rot = c(0)
)

# Row annotation: wilcoxon p-values
# make sure that genes in rows were arranged by Gini score from high to low
ha.row.pval <- rowAnnotation(p.value = anno_points(-log2(rowdat$wilcox.pvalue), which = 'row',
                                                   gp = gpar(col = 'black'),
                                                   # ylim = c(0,0.05),
                                                   axis_param = list(gp = gpar(fontsize = 5,
                                                                               family = 'Arial'),
                                                                     side = 'bottom'),
                                                   # axis_direction = 'normal', # 'reverse'
                                                   axis = TRUE),
                             width = unit(1.5, 'cm'),
                             show_annotation_name = TRUE,
                             annotation_legend_param = list(direction = 'horizontal', nrow = 1),
                             annotation_name_gp = gpar(fontsize = 10),
                             annotation_name_offset = unit(c(6), 'mm'),
                             annotation_name_rot = c(0)
)

rowdat$ratio.color <- ifelse(rowdat$ratio < 1, 'green','red')

ha.row.ratio <- rowAnnotation(expr.ratio = anno_points(rowdat$ratio, which = 'row',
                                                   gp = gpar(col = rowdat$ratio.color),
                                                   # ylim = c(-3,3),
                                                   axis_param = list(gp = gpar(fontsize = 5,
                                                                               family = 'Arial'),
                                                                     side = 'bottom'),
                                                   # axis_direction = 'normal', # 'reverse'
                                                   axis = TRUE),
                             width = unit(1.5, 'cm'),
                             show_annotation_name = TRUE,
                             annotation_legend_param = list(direction = 'horizontal', nrow = 1),
                             annotation_name_gp = gpar(fontsize = 10),
                             annotation_name_offset = unit(c(6), 'mm'),
                             annotation_name_rot = c(0)
)

# create row annotation of cancer hallmark
hm.dat <- df.hallmark %>% subset(Cell == my.drug & p.adjust < 0.05) %>% arrange(-NES)
hm.order <- hm.dat$Description
hm.order <- factor(hm.order, levels = hm.order)

# create dat.freq
temp.freq <- allHallmarks %>% subset(Drug == my.drug & Gene %in% rowdat$Gene)
dat.freq <- reshape2::dcast(temp.freq, Gene ~ Hallmark.ID)
# convert NA to 0 and others to 1
dat.freq[is.na(dat.freq)] <- 0
dat.freq <- tibble::column_to_rownames(dat.freq, var = 'Gene')
dat.freq[dat.freq > 0] <-1

# scale gene expression level across cell lines
dset.mat <- dset.cca[,-c(which(colnames(dset.cca) == 'Drug'))]
mat <- t(apply(dset.mat, 1, scale))
colnames(mat) <- colnames(dset.mat)
mat <- as.data.frame(mat)

mat <- mat[rowdat$Gene,] 

if (nrow(mat) > 50) {
  mat <- mat[1:50,]
} else {
  mat <- mat
}

# rearrange rows and columns
dat.freq.2 <- dat.freq[rownames(mat),as.character(hm.order)]
# delete prefix characters
colnames(dat.freq.2) <- gsub('HALLMARK_','',colnames(dat.freq.2)) %>% trimws(., which = 'both')

fq.hm <- ComplexHeatmap::Heatmap(as.data.frame(dat.freq.2), 
                 name = 'hallmark', 
                 col = c('white','black'), 
                 cluster_rows = FALSE, 
                 row_title = NULL, 
                 cluster_columns = FALSE, 
                 show_row_names = TRUE,
                 row_names_side = 'left',
                 column_names_gp = gpar(fontsize = 10, family = 'Arial'),
                 rect_gp = gpar(col = 'gray80', lwd = 1),
                 # heatmap_legend_param = list(title = "Methylation"), 
                 width = ncol(dat.freq.2)*unit(4, "mm"))


# Plot heatmap

bio.hm <- Heatmap(as.matrix(mat), # my.dt.sorted
                  # km = 2,
                  # split = 2,
                  # gap = unit(2,'mm'),
                  # row_gap = gap,
                  row_names_side = 'right',
                  cluster_rows = FALSE, 
                  # clustering_distance_rows = 'euclidean', 
                  # clustering_method_rows = 'ward.D2',
                  # show_row_dend = FALSE,
                  cluster_columns = FALSE, 
                  # clustering_distance_columns = 'euclidean', 
                  # clustering_method_columns = 'ward.D2',
                  # show_column_dend = FALSE,
                  column_names_gp = gpar(fontsize = 10, family = 'Arial'),
                  row_names_gp = gpar(fontsize = 10, family = 'Arial'),
                  top_annotation = ha,
                  # top_annotation_height = unit.c(unit(2, 'cm'), unit(2, 'cm'), unit(2, 'cm')),
                  col = circlize::colorRamp2(c(-4,-3,-2,-1,0,1,2,3,4), my.colorgradient3),
                  heatmap_legend_param = list(
                    color_bar = 'discrete',
                    direction = 'horizontal',nrow = 1),
                  column_title = paste0('Classified by \n',gsub('_S.R','',my.drug),' GR50'),
                  name = 'expr.level' # legend title
)

ComplexHeatmap::draw(fq.hm + bio.hm + ha.row.ratio + ha.row.pval + ha.row.VIPrf + ha.row.VIPplsda)

```

```{r}
setwd('C:/Users/patipark/Dropbox/CCA project/CCA RNA-seq/NewGeneSet_Module_InitialAnalysis/Figure_4A_files')
pdf(paste0('BiomarkersIdentification_Fig4A_byPval_20200408.pdf'),
    paper = 'A4',
    width = 7, #inches
    height = 12, #inches
    useDingbats = FALSE  #avoid letters instead of point objects
)
  ComplexHeatmap::draw(fq.hm + bio.hm + ha.row.ratio + ha.row.pval + ha.row.VIPrf + ha.row.VIPplsda,
       # annotation_legend_list = lgd_list,
       # row_title = '', 
       # column_title = '',
       heatmap_legend_side = 'bottom', 
       annotation_legend_side = 'bottom')
  # decorate_annotation('log10GR50', {
  #     grid.lines(c(0, 1), unit(c(0, 0), 'native'), gp = gpar(col = 'black'))
  # })
  dev.off()
  
# }
```

Figure 4B
Overlaps of biomarkers using Node-edge network
nodes = drugs
edge = overlapping genes
```{r}
require(GGally)
require(ggnetwork)
require(sna)
require(network)

DrugNodes <- c('Subtype_1.2',
               'Saracatinib','TAK733','Dasatinib',
               'Gemcitabine','Cisplatin','FiveFU') #'OrgSubtype_1.2'
Drug1 <- c('Saracatinib','TAK733','Dasatinib',
           'Gemcitabine','Cisplatin','FiveFU')

# subset significant gene biomarkers from Classifier.genes table
X <- Classifier.genes %>% subset(Drug %in% DrugNodes)

# findOverlap <- function(X){
# X = list of genes in a drug
my.drugs <- DrugNodes
# define center drug
center.drug <- 'Subtype_1.2'
# find number of drugs
n <- as.numeric(length(my.drugs))

# create coordinates (x,y)
# coords <- expand.grid(1:5,1:5)
my.edges <- lapply(1:n, function(x) {
  # x <- 1
  if (x < n){
    corX <- rep(n-x,x)
    nx <- n-(x-1)
    corY <- c(nx:n)
    x <- x+1
    out <- data.frame('from' = corX,
                      'to' = corY)
  } else {
    out <- data.frame('from' = NA,
                      'to' = NA)
  }
  return(out)
})
# build edge.list
edge.list <- do.call(rbind,my.edges)
# remove NA rows
edge.list <- edge.list %>% subset(rownames(.) %in% which(!is.na(edge.list$from))) %>% as.data.frame()
edge.list$from <- as.integer(edge.list$from)
# build node.list
node.list <- c(center.drug,my.drugs[c(which(my.drugs != center.drug))])
node.list <- data.frame('id' = c(1:n),
                        'label' = node.list)
node.list$label <- as.character(node.list$label)
node.list$label <- ifelse(node.list$label == 'Subtype_1.2','CCA Subtype 1',
                          ifelse(node.list$label == 'OrgSubtype_1.2','Pancreas cancer-like', node.list$label))

node.list$node.colors <- ifelse(node.list$label %in% Drug1,'D1',
                                ifelse(node.list$label == 'Pancreas cancer-like', 'D3',
                                       ifelse(node.list$label == 'CCA Subtype 1','D0','D2')))
# count number of genes in each node
vert <- X %>% group_by(Drug) %>% summarise(n = n())
vert$Drug <- gsub('Subtype_1.2','CCA Subtype 1', vert$Drug)
node.list$n <- vert$n[match(node.list$label,vert$Drug)]

# build table for Genes
dat <- lapply(1:n, function(p) {
  temp <- X %>% subset(Drug %in% my.drugs[p])
  Gene <- temp$Gene
  Drug <- my.drugs[p]
  
  dat.out <- data.frame('Drug' = Gene)
  colnames(dat.out) <- Drug
  
  return(dat.out)
})

# function for edges
cbind.fill <- function(...){
  nm <- list(...) 
  nm <- lapply(nm, as.matrix)
  n <- max(sapply(nm, nrow)) 
  do.call(cbind, lapply(nm, function (x) 
    rbind(x, matrix(, n-nrow(x), ncol(x))))) 
}

dset <- do.call(cbind.fill,dat)

# find overlapping genes
count.ov <- lapply(1:nrow(edge.list), function(d) {
  # d <- 1
  # select gene set A
  A <- dset[,edge.list[d,1]]
  # remove NA
  A <- A[!is.na(A)]
  # select gene set B
  B <- dset[,edge.list[d,2]]
  # remove NA
  B <- B[!is.na(B)]
  # count numbe of overlapped genes
  AxB <- length(intersect(A,B))
  return(AxB)
})

wt <- as.vector(do.call(rbind,count.ov))

# append to edge.list table
edge.list2 <- tibble::add_column(edge.list,wt,.after = 2) %>% as.data.frame()
colnames(edge.list2) <- c('from','to','wt')

# define node colors
node.cols <- node.list
# 
# Drug1 <- c('PD318088','PD0325901','TAK733','Selumetinib','Ribociclib',
#            'RO3306','Saracatinib','Bosutinib','Vandetanib','Dasatinib',
#            'Azacitidine','Gefitinib','Lapatinib','Erlotinib','Afatinib',
#            'Omipalisib','Momelotinib','Vorinostat','Nilotinib','Imatinib',
#            'Masitinib','NVP-AEW541','Birinapant','Sunitinib','BGJ398-Nov',
#            'Palbociclib','Fedratinib','Pacritinib','LY294002','I-BET',
#            'Abemaciclib','JQ1','Fludarabine')
# 
node.cols$colors <- node.list$node.colors
# replace number with label
# edge.list$from <- node.list$label[match(edge.list$from,node.list$id)]
# edge.list$to <- node.list$label[match(edge.list$to,node.list$id)]
# 

# plot figure
require(tidygraph)
require(ggraph)
require(network)
require(igraph)

routes_tidy <- tbl_graph(nodes = node.list, 
                         edges = edge.list2, 
                         directed = TRUE)

routes_tidy <- delete.edges(routes_tidy, which(E(routes_tidy)$wt == 0))

layout <- create_layout(routes_tidy, layout = 'igraph', algorithm = 'nicely')

# add factor level to label
layout$label <- factor(layout$label, 
                       levels = c('CCA Subtype 1',
                                  'Saracatinib','TAK733','Dasatinib',
                                  'Gemcitabine','Cisplatin','FiveFU'))
# layout$node.colors <- node.cols$colors[match(layout$label,node.cols$label)] %>% as.factor()

Fig4B <- ggraph(routes_tidy, 
                   layout = 'linear',
                   circular = TRUE
) + 
  geom_edge_arc(aes(width = wt),color = 'gray50', alpha = 0.8) +
  scale_edge_width(range = c(0, 5)) +
  geom_node_point(aes(color = as.factor(label),
                      size = n),
                  # size = 12,
                  show.legend = FALSE) +
  scale_size(range = c(5,15)) +
  scale_color_manual(
    limits = as.factor(layout$label),
    values = c('CCA Subtype 1' = 'gray',
               'Saracatinib' = 'cyan',
               'TAK733' = 'cyan',
               'Gemcitabine' = 'orange',
               'Cisplatin' = 'orange',
               'FiveFU' = 'orange',
               'Dasatinib' = 'cyan',
               'Pancreas cancer-like' = 'gray')
  ) +
  geom_node_text(aes(label = paste0(label,' (',n,')')),
                 size = 4,
                 nudge_y = -0.2,
                 nudge_x = 0,
                 repel = TRUE,
                 show.legend = FALSE) +
  labs(edge_width = "Overlap size") +
  theme_graph() +
  theme(
    text = element_text(family = 'Arial', size = 10),
    legend.position = 'bottom'
  )

# }
```

Save figure 4C
```{r}
setwd('C:/Users/patipark/Dropbox/CCA project/CCA RNA-seq/NewGeneSet_Module_InitialAnalysis/Figure_4A_files')
ggsave(Fig4B,
       filename = 'Fig4B_20200408.pdf',
       height = 18,
       width = 15,
       units = 'cm',
       device = cairo_pdf
       )

# png('FigS6AC_20191021.png', 
#     family = 'Arial',
#     width = 42, 
#     height = 25, 
#     units = 'cm', 
#     res = 600)
# draw(FigS6A,
#      # annotation_legend_list = lgd_list,
#      # row_title = '', 
#      # column_title = '',
#      heatmap_legend_side = 'bottom', 
#      annotation_legend_side = 'bottom')

dev.off()
```